%-------------------------
% Resume in Latex
% Author : RAJAT RANJAN
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}




\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    {\Huge \scshape RAJAT RANJAN} \\ \vspace{1pt}
    D E V E L O P E R \\ \vspace{3pt} 
    \small \raisebox{-0.1\height}\faPhone\ +91 9695591973 ~ ~ \href{mailto:rajatranjanrai@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{rajatranjanrai@gmail.com}} ~ ~ 
    \href{https://www.linkedin.com/in/rajatranjanrai/}{\raisebox{-0.2\height}\faLinkedin\ \underline{rajatranjanrai}}  ~ ~
    \href{https://github.com/rajatranjanrai}{\raisebox{-0.2\height}\faGithub\ \underline{rajatranjanrai}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Visvesvaraya Technological University}{Aug. 2019 -- July 2023}
      {Bachelor of Engineering in Computer Science}{Bangalore, Karnataka}
      \resumeSubheading
      {Tulsi Vidya Niketan}{Apr. 2019}
      {Intermediate}{Varanasi, UttarPradesh}
      \resumeSubheading
      {Tulsi Vidya Niketan}{Apr. 2019}
      {High-school}{Varanasi, UttarPradesh}
  \resumeSubHeadingListEnd

%-----------Technical Skills-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{
        \item \textbf{Languages:} HTML, CSS, JavaScript, C, Python
        \vspace{3pt}
        \item \textbf{Technologies and Frameworks:} GitHub, VScode, Jupiter, Eclipse, Google Cloud Platform, Android Studio, Ms-Office, PowerBI, Tailwindcss, Bootstrap, MySQL
        \vspace{3pt}
        \item \textbf{Interest:} Web Design, Web Development, Web Technologies, Problem Solving, Creativity and Innovations
    }
\end{itemize}
\vspace{-10pt}




%-----------Internship Projects-----------
\section{Internship Projects}
\resumeSubHeadingListStart

\vspace{5pt}
\resumeSubheading
{3D Model Gallery}{\textit{February 2024}}
{Web Development}{Resonance3D Pvt. Ltd.}
\resumeItemListStart
    \resumeItem{Utilized skills: HTML, CSS, JavaScript, GLB 3D Model, AR/VR Viewer.}
    \resumeItem{Developed and implemented a live project to create immersive experiences.}
    \resumeItem{Integrated GLB 3D Models to enable users to visualize objects within their space.}
    \resumeItem{Source Code: \href{https://github.com/rajatranjanrai/3D-Model-Gallery.git}{\textit{\underline{https://github.com/rajatranjanrai/3D-Model-Gallery.git}}}}
    \resumeItem{Live Demo: \href{https://3dmodels.resonance3d.com}{\textit{\underline{https://3dmodels.resonance3d.com}}}}
\resumeItemListEnd

\vspace{5pt}
\resumeSubheading
{Quora for Engineering Queries}{\textit{August 2022}}
{Web Development}{Compsoft Technologies}
\resumeItemListStart
    \resumeItem{Utilized Skills: HTML, CSS, JavaScript, Python, Node.js.} \\
    \resumeItem{Developed a user-friendly platform enabling students to connect with senior engineers.} \\
    \resumeItem{Facilitated seamless communication and knowledge exchange within the engineering community.} \\
    \resumeItem{Source Code: \href{https://github.com/rajatranjanrai/Clone-Quora-.git}{\textit{\underline{https://github.com/rajatranjanrai/3D-Model-Gallery.git}}}} \\
    \resumeItem{Live Demo: \href{https://nikhilraj060.github.io/quora-clone/}{\textit{\underline{https://rajatranjanrai.github.io/quora-clone/}}}}
\resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-5pt}



%-----------PROJECTS-----------
\section{Individual Projects}
    \vspace{5pt}
    \resumeSubheading
          {SpaceX Re-design  FALCON 9}{\textit{October 2023}}
          {Developer}{}
          \resumeItemListStart
            \resumeItem{Skills Utilized: HTML, CSS (Tailwind), JavaScript}
            \resumeItem{Undertook SpaceX redesign project with a focus on providing comprehensive information about Falcon 9.}
            \resumeItem{Implemented Tailwind CSS framework to ensure responsive and visually appealing design.}
            \resumeItem{Source Code: \href{https://github.com/rajatranjanrai/Falcon-9.git}{\textit{\underline{https://github.com/rajatranjanrai/Falcon-9.git}}}}
            \resumeItem{Live Demo: \href{https://rajatranjan-falcon-9.netlify.app}
            {\textit{\underline{https://rajat-redesign-specex-falcon9}}}}
          \resumeItemListEnd
    \vspace{5pt}


    \resumeSubheading
{Easy Bank Landing Page (From FrontEnd Mentor)}{\textit{July 2023}}
{Developer}{}
\resumeItemListStart
    \resumeItem{Skills Utilized: HTML, CSS, JavaScript. Enhanced user interaction and functionality using JavaScript.}
    \resumeItem{Designed and developed a fully responsive landing page for Easy Bank, meeting FrontEnd Mentor's specifications.}
    \resumeItem{Implemented HTML and CSS to create a visually appealing layout, ensuring compatibility with various screen sizes.}
    \resumeItem{SrcCode: \href{https://github.com/rajatranjanrai/EASY-BANKING-Lending-Page.git}{\textit{\underline{https://github.com/rajatranjanrai/EASY-BANKING-Lending-Page.git}}}}
    \resumeItem{Live Demo: \href{https://rajat-easybanking.netlify.app/}{\textit{\underline{https://rajat-easybanking.netlify.app/}}}}
\resumeItemListEnd

\vspace{5pt}



%%-----------INTERNSHIPS-----------
\section{INTERNSHIPS}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Resonance3D Pvt. Ltd.}{January 2024 -- March 2024}
      {Web Developer}{}
    \resumeSubheading
      {Compsoft Technologies}{August 2022 -- September 2022}
      {Full Stack Web Development}{}
  \resumeSubHeadingListEnd


%%-----------CERTIFICATIONS-----------
\section{CERTIFICATIONS}
\resumeSubHeadingListStart
    \resumeSubheading
      {Course on HTML}{2021}
      {\href{http://ude.my/UC-64198ff3-c0cd-4354-922b-a0c610b02116}{\underline{Certificate Verification Link}}}{UDEMY}
    \resumeSubheading
      {Course on CSS}{2021}
      {\href{http://ude.my/UC-64198ff3-c0cd-4354-922b-a0c610b02116}{\underline{Certificate Verification Link}}}{UDEMY}
    \resumeSubheading
      {Course on JAVASCRIPT}{2021}
      {\href{http://ude.my/UC-64198ff3-c0cd-4354-922b-a0c610b02116}{\underline{Certificate Verification Link}}}{UDEMY}
    \resumeSubheading
      {Course on C Fundamentals}{2021}
      {\href{}{\underline{Certificate Verification Link}}}{UDEMY}
    \resumeSubheading
      {Course on Python}{2021}
      {\href{http://ude.my/UC-3b24818b-b8cd-4e6d-86d4-5f554d9f8580}{\underline{Certificate Verification Link}}}{UDEMY}
\resumeSubHeadingListEnd




%------Strength-------
\section{Strength}
    \resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item Strong communication
                \item Skilled problem-solver
                \item Strong team player
                \item Quick learner
                \item Innovative thinker
                \item Self-motivated
                \item Result Oriented 
                \item Leadership
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    \resumeSubHeadingListEnd

\end{document}
